Measuring Software Ticket Quality using Quantitative Data Analysis

### 2018-04-19 paper/paper.tex
Complete the related work section

>>>>

Another overall aspect of software tickets and issue tracking systems that could be improved through 
determining the quality factors for tickets is automatically assigning a bug report or a feature request 
to the most suitable developer (or team of developers). Anvik et. al \cite{anvik2011reducing}
propose a Machine Learning technique that could automatically assign a bug report to the developer 
with the most expertise in that specific area. Firstly, the algorithm takes as input various types of information from 
tickets: textual description and summary, operating system used when the bug occurred, developer 
who owns the source code, which developers have lighter workloads at that point in time etc. After the 
tool was evaluated, the authors concluded that it can be used in production as it provides a high 
rate of accuracy when assigning the developers, but it needs more data so that the model is trained 
properly.
